\textbf{COMPARISON OF \\ HEURISTIC ALGORITHMS \\ FOR KP01} \\[0.5cm] \rule{12cm}{0.3mm} \\[0.5cm] \small \scshape{A comparison of heuristic algorithms for solving the 0-1 Knapsack Problem} \\[0.4cm] \rule{12cm}{0.3mm} \vskip -0.3cm

### 2023-04-20 doc/paper.tex
added percent deviations in the results

\begin{table}[h!]\centering
    \caption{Mean and StDev. of 100 Randomized items} \label{100-mean}
    \begin{tabu}{|c|[1pt]c|c|c|c|c|c|}
        \tabucline[1pt]{1-6} 
        Testcase & 1 & 2 & 3 & 4 & 5 \\ [-1pt] \tabucline[1pt]{1-6} 
        Harmony Mean &4160.33 &2561 &5288 &3535 &1747 \\ \hline
        Harmony StDev. &3.50 &0 &19.66 &0 &0 \\ [-1pt] \tabucline[1pt]{1-6}
        BMQHOA Mean &3926.83 &2561 &4879 &3360.66 &1711.5 \\ \hline
        BMQHOA StDev. &40.27 &0 &46.18 &68.96 &25.71 \\[-1pt] \tabucline[1pt]{1-6}
    \end{tabu}

@@

    \caption{Mean and StDev. of 1000 Randomized items} \label{1000-mean}
    \begin{tabu}{|c|[1pt]c|c|c|c|c|c|}
        \tabucline[1pt]{1-6} 
        Testcase & 1 & 2 & 3 & 4 & 5 \\ [-1pt] \tabucline[1pt]{1-6} 
        Harmony Mean &156083.83 &118603.83 &144070 &109734.33 &126366.16 \\ \hline
        Harmony StDev. &830.04 &1904.69 &1343.77 &1037.03 &1236.73 \\ [-1pt] \tabucline[1pt]{1-6}
        BMQHOA Mean &145086.5 &109876.33 &136622.66 &101951.33 &118291.16 \\ \hline
        BMQHOA StDev. &1035.45 &1540.63 &2042.95 &1271.88 &799.78 \\ [-1pt] \tabucline[1pt]{1-6}
    \end{tabu}

@@

    \caption{Mean and StDev. of 10k Randomized items} \label{10k-mean}
    \begin{tabu}{|c|[1pt]c|c|c|c|c|c|}
        \tabucline[1pt]{1-6} 
        Testcase & 1 & 2 & 3 & 4 & 5 \\ [-1pt] \tabucline[1pt]{1-6} 
        Harmony Mean &7681910.33 &10567302 &8014906 &9347061.66&9583139.16\\ \hline
        Harmony StDev. &51555.39&23956.31&39449.15&56967.66&55816.60\\ [-1pt] \tabucline[1pt]{1-6}
        BMQHOA Mean &7438487.16&10276681.83&7774520.83&9075476 &9330322.16\\ \hline
        BMQHOA StDev. &29887.17&50507.35&34559.10&53168.02&46301.35\\ [-1pt] \tabucline[1pt]{1-6}
    \end{tabu}
\end{table}

   % \vspace{1cm}
\begin{table}
    \centering
    \caption{Mean and StDev. of Uncorrelated Dataset} \label{uncorrelated-mean}
    \begin{tabu}{|c|[1pt]c|c|c|c|c|c|}
        \tabucline[1pt]{1-6} 
        Testcase & 1 & 2 & 3 & 4 & 5 \\ [-1pt] \tabucline[1pt]{1-6} 
        Harmony Mean &9147 &11238 &51019.5 &99036.16&448975 \\ \hline
        Harmony StDev. &0 &0 &437.85&1544.34&1135.46\\ [-1pt] \tabucline[1pt]{1-6}
        BMQHOA Mean &8974.5 &10976.5 &47401.5 &91725.83&431259.66\\ \hline
        BMQHOA StDev. &147.24&154.37&841.75&1346.23&3049.43\\ [-1pt] \tabucline[1pt]{1-6}
    \end{tabu}

@@

    \caption{Mean and StDev. of Weakly Correlated Dataset} \label{weakly-mean}
    \begin{tabu}{|c|[1pt]c|c|c|c|c|c|}
        \tabucline[1pt]{1-6} 
        Testcase & 1 & 2 & 3 & 4 & 5 \\ [-1pt] \tabucline[1pt]{1-6} 
        Harmony Mean &1514 &1627.66&8907.33&17371.83&82681.33\\ \hline
        Harmony StDev. &0 &2.42&27.56&126.76&390.98\\ [-1pt] \tabucline[1pt]{1-6}
        BMQHOA Mean &1508.16&1613.66&8435.33&16539 &80900.66\\ \hline
        BMQHOA StDev. &6.82&16.74&60.60&133.95&970.71\\ [-1pt] \tabucline[1pt]{1-6}
    \end{tabu}

@@

    \caption{Mean and StDev. of Strongly Correlated Dataset} \label{strongly-mean}
    \begin{tabu}{|c|[1pt]c|c|c|c|c|c|}
        \tabucline[1pt]{1-6} 
        Testcase & 1 & 2 & 3 & 4 & 5 \\ [-1pt] \tabucline[1pt]{1-6} 
        Harmony Mean &2391.66&2697 &13682.5 &26444.66&126448 \\ \hline
        Harmony StDev. &6.08&0 &60.05&240.84&615.61\\ [-1pt] \tabucline[1pt]{1-6}
        BMQHOA Mean &2327.33&2658.66&13334.66&25604 &123813.83\\ \hline
        BMQHOA StDev. &48.55&48.81&182.91&91.32&773.19\\ [-1pt] \tabucline[1pt]{1-6}
    \end{tabu}
\end{table}

%100 randomized items mean and stdev graph
\begin{figure}[hbt!]
\centering
    \begin{tikzpicture}
        \begin{axis} [
            ybar = .05cm,
            bar width = 12pt,
            xmin = 1,
            xmax = 6,
            %ytick = data,
            y tick label style={
            /pgf/number format/1000 sep=},
            enlarge y limits = {value = .25, upper},
            enlarge x limits = {abs = .8}
        ]
        \addplot+ [
                error bars/.cd,
                    y dir=both,
                    % (changed from `y explicit` so the error bars are (clearly) visible
                    y explicit ,
            ] coordinates {
                (1, 4160.33) +- (0,3.5)
                (2, 2561) +- (0,0)
                (3, 5288) +- (0,19.667)
                (4,3535) +- (0,0)
                (5,1747) +- (0,0)
                (6,1) +- (0, 0)
            };
        \addplot+ [
                error bars/.cd,
                    y dir=both,
                    % (changed from `y explicit` so the error bars are (clearly) visible
                    y explicit ,
            ] coordinates {
                (1, 3926.83) +- (0,40.27613023)
                (2, 2561) +- (0,0)
                (3, 4879) +- (0,46.18224767)
                (4,3360.66) +- (0,68.9627919)
                (5,1711.5) +- (0,25.71186497)
                (6,1) +- (0, 0)
            };
        \legend {DGHS, BMQHOA};
        \end{axis}
    \end{tikzpicture}
    \caption{Mean of profit values for 100 randomized items} \label{100-graph}
\end{figure}

%1000 random items mean and stdev graph
\begin{figure}[hbt!]
\centering
    \begin{tikzpicture}
        \begin{axis} [
            ybar = .05cm,
            bar width = 12pt,
            xmin = 1,
            xmax = 6,
            %ytick = data,
            y tick label style={
            /pgf/number format/1000 sep=},
            enlarge y limits = {value = .25, upper},
            enlarge x limits = {abs = .8}
        ]
        \addplot+ [
                error bars/.cd,
                    y dir=both,
                    % (changed from `y explicit` so the error bars are (clearly) visible
                    y explicit ,
            ] coordinates {
                (1, 156083.83) +- (0,830.04)
                (2, 118603.83) +- (0,1904.70)
                (3, 144070.00) +- (0,1343.77)
                (4, 109734.33) +- (0,1037.03)
                (5, 126366.17) +- (0,1236.73)
                (6,1) +- (0, 0)
            };
        \addplot+ [
                error bars/.cd,
                    y dir=both,
                    % (changed from `y explicit` so the error bars are (clearly) visible
                    y explicit ,
            ] coordinates {
                (1, 145086.50) +- (0,1035.46)
                (2, 109876.33) +- (0,1540.63)
                (3, 136622.67) +- (0,2042.95)
                (4,101951.33) +- (0,1271.88)
                (5,118291.17) +- (0,799.79)
                (6,1) +- (0, 0)
            };
        \legend {DGHS, BMQHOA};
        \end{axis}
    \end{tikzpicture}
\caption{Mean of profit values for 1000 randomized items} \label{1000-graph}
%\end{figure}

%10k random items mean and stdev graph
%\begin{figure}[hbt!]
%\centering
    \begin{tikzpicture}
        \begin{axis} [
            ybar = .05cm,
            bar width = 12pt,
            xmin = 1,
            xmax = 6,
            %ytick = data,
            y tick label style={
            /pgf/number format/1000 sep=},
            enlarge y limits = {value = .25, upper},
            enlarge x limits = {abs = .8}
        ]
        \addplot+ [
                error bars/.cd,
                    y dir=both,
                    % (changed from `y explicit` so the error bars are (clearly) visible
                    y explicit ,
            ] coordinates {
                (1, 7681910.333) +- (0, 51555.40)
                (2, 10567302) +- (0, 23956.32)
                (3, 8014906) +- (0, 39449.15)
                (4, 9347061.67) +- (0, 56967.67)
                (5, 9583139.17) +- (0, 55816.61)
                (6,1) +- (0, 0)
            };
        \addplot+ [
                error bars/.cd,
                    y dir=both,
                    % (changed from `y explicit` so the error bars are (clearly) visible
                    y explicit ,
            ] coordinates {
                (1, 7438487.17) +- (0, 29887.18)
                (2, 10276681.83) +- (0, 50507.36)
                (3, 7774520.83) +- (0, 34559.11)
                (4, 9075476.00) +- (0, 53168.02)
                (5, 9330322.17) +- (0, 46301.35)
                (6, 1) +- (0, 0)
            };
        \legend {DGHS, BMQHOA};
        \end{axis}
    \end{tikzpicture}
\caption{Mean of profit values for 10k randomized items} \label{10k-graph}
\end{figure}

%uncorrelated items mean and stdev graph
\begin{figure}[hbt!]
    \centering
    \begin{tikzpicture}
        \begin{axis} [
            ybar,
            bar width = 12pt,
            width = 14cm,
            height = 6cm,
            xmin = 1,
            xmax = 6,
            %x tick label style={rotate=45},
            xtick = data,
            %ytick = data,
            y tick label style={/pgf/number format/1000 sep=},
            enlarge y limits = {value = .25, upper},
            legend cell align={left},
            enlarge x limits = {abs = .8}
            %enlarge x limits = {abs = .8}
        ]
        \addplot+ [
                error bars/.cd,
                    y dir=both,
                    % (changed from `y explicit` so the error bars are (clearly) visible
                    y explicit ,
            ] coordinates {
                (1, 9147) +- (0, 0.00)
                (2, 11238.00) +- (0, 0.00)
                (3, 51019.50) +- (0, 437.85)
                (4, 99036.17) +- (0, 1544.34)
                (5, 448975.00) +- (0, 1135.46)
                (6, 0) +- (0, 0)
            };
        \addplot+ [
                error bars/.cd,
                    y dir=both,
                    % (changed from `y explicit` so the error bars are (clearly) visible
                    y explicit ,
            ] coordinates {
                (1, 8974.50) +- (0, 147.24)
                (2, 10976.50) +- (0, 154.37)
                (3, 47401.50) +- (0, 841.76)
                (4, 91725.83) +- (0, 1346.24)
                (5, 431259.67) +- (0, 3049.43)
                (6, 0) +- (0, 0)
            };
        \legend {DGHS, BMQHOA};
        \end{axis}
    \end{tikzpicture}
\caption{Mean of profit values for uncorrelated items} \label{uncorrelated-graph}
%\end{figure}

%\begin{figure}[hbt!]
    %\centering
    \begin{tikzpicture}
        \begin{axis} [
            ybar,
            bar width = 12pt,
            width = 14cm,
            height = 6cm,
            xmin = 1,
            xmax = 6,
            %x tick label style={rotate=45},
            xtick = data,
            %ytick = data,
            y tick label style={/pgf/number format/1000 sep=},
            enlarge y limits = {value = .25, upper},
            legend cell align={left},
            enlarge x limits = {abs = .8}
            %enlarge x limits = {abs = .8}
        ]
        \addplot+ [
                error bars/.cd,
                    y dir=both,
                    % (changed from `y explicit` so the error bars are (clearly) visible
                    y explicit ,
            ] coordinates {
                (1, 1514) +- (0, 0.00)
                (2, 1627.666667) +- (0, 2.422120283)
                (3, 8907.333333) +- (0, 27.56567914)
                (4, 17371.83333) +- (0, 126.7665834)
                (5, 82681.33333) +- (0, 390.9842282)
                (6, 0) +- (0, 0)
            };
        \addplot+ [
                error bars/.cd,
                    y dir=both,
                    % (changed from `y explicit` so the error bars are (clearly) visible
                    y explicit ,
            ] coordinates {
                (1, 1508.166667) +- (0, 6.823977335)
                (2, 1613.666667) +- (0, 16.74116683)
                (3, 8435.333333) +- (0, 60.6025302)
                (4, 16539) +- (0, 133.9596954)
                (5, 80900.66667) +- (0, 970.7196643)
                (6, 0) +- (0, 0)
            };
        \legend {DGHS, BMQHOA};
        \end{axis}
    \end{tikzpicture}
\caption{Mean of profit values for weakly correlated items} \label{weakly-graph}
%\end{figure}

%\begin{figure}[hbt!]
    %\centering
    \begin{tikzpicture}
        \begin{axis} [
            ybar,
            bar width = 12pt,
            width = 14cm,
            height = 6cm,
            xmin = 1,
            xmax = 6,
            %x tick label style={rotate=45},
            xtick = data,
            %ytick = data,
            y tick label style={/pgf/number format/1000 sep=},
            enlarge y limits = {value = .25, upper},
            legend cell align={left},
            enlarge x limits = {abs = .8}
            %enlarge x limits = {abs = .8}
        ]
        \addplot+ [
                error bars/.cd,
                    y dir=both,
                    % (changed from `y explicit` so the error bars are (clearly) visible
                    y explicit ,
            ] coordinates {
                (1, 2391.666667) +- (0, 6.08824003)
                (2, 2697) +- (0, 0)
                (3, 13682.5) +- (0, 60.05580738)
                (4, 26444.66667) +- (0, 240.8407496)
                (5, 126448) +- (0, 615.61384)
                (6, 0) +- (0, 0)
            };
        \addplot+ [
                error bars/.cd,
                    y dir=both,
                    % (changed from `y explicit` so the error bars are (clearly) visible
                    y explicit ,
            ] coordinates {
                (1, 2327.333333) +- (0, 48.55375028)
                (2, 2658.666667) +- (0, 48.81666382)
                (3, 13334.66667) +- (0, 182.9160099)
                (4, 25604) +- (0, 91.32579044)
                (5, 123813.8333) +- (0, 773.1955553)
                (6, 0) +- (0, 0)
            };
        \legend {DGHS, BMQHOA};
        \end{axis}
    \end{tikzpicture}
\caption{Mean of profit values for strongly correlated items} \label{strongly-graph}
\end{figure}

>>>>

\begin{table}[h!]\centering
    \caption{Mean and StDev. of 100 Randomized items} \label{100-mean}
    \begin{tabu}{|c|[1pt]c|c|c|c|c|c|}
        \tabucline[1pt]{1-6} 
        Testcase & 1 & 2 & 3 & 4 & 5 \\ [-1pt] \tabucline[1pt]{1-6} 
        DGHS Mean &4160.33 &2561 &5288 &3535 &1747 \\ \hline
        DGHS StDev. &3.50 &0 &19.66 &0 &0 \\ \hline
        Mean Percent deviation from optimal &0.21 &0.00 &0.40 &0.00 &0.00 \\ [-1pt] \tabucline[1pt]{1-6}
        BMQHOA Mean &3926.83 &2561 &4879 &3360.66 &1711.5 \\ \hline
        BMQHOA StDev. &40.27 &0 &46.18 &68.96 &25.71 \\ \hline
        Mean Percent deviation from optimal &5.80&0 &8.09&4.93&2.03\\ [-1pt] \tabucline[1pt]{1-6}
    \end{tabu}

@@

    \caption{Mean and StDev. of 1000 Randomized items} \label{1000-mean}
    \begin{tabu}{|c|[1pt]c|c|c|c|c|c|}
        \tabucline[1pt]{1-6} 
        Testcase & 1 & 2 & 3 & 4 & 5 \\ [-1pt] \tabucline[1pt]{1-6} 
        DGHS Mean &156083.83 &118603.83 &144070 &109734.33 &126366.16 \\ \hline
        DGHS StDev. &830.04 &1904.69 &1343.77 &1037.03 &1236.73 \\ \hline
        Mean Percent deviation from optimal &13.71&11.76&14.12&10.77&13.27\\ [-1pt] \tabucline[1pt]{1-6}
        BMQHOA Mean &145086.5 &109876.33 &136622.66 &101951.33 &118291.16 \\ \hline
        BMQHOA StDev. &1035.45 &1540.63 &2042.95 &1271.88 &799.78 \\ \hline
        Mean Percent deviation from optimal &19.79&18.25&18.56&17.10&18.82\\ [-1pt] \tabucline[1pt]{1-6}
    \end{tabu}

@@

    \caption{Mean and StDev. of 10k Randomized items} \label{10k-mean}
    \begin{tabu}{|c|[1pt]c|c|c|c|c|c|}
        \tabucline[1pt]{1-6} 
        Testcase & 1 & 2 & 3 & 4 & 5 \\ [-1pt] \tabucline[1pt]{1-6} 
        DGHS Mean &7681910.33 &10567302 &8014906 &9347061.66&9583139.16\\ \hline
        DGHS StDev. &51555.39&23956.31&39449.15&56967.66&55816.60\\ \hline 
        Mean Percent deviation from optimal &22.61&23.11&22.07&23.10&23.00\\[-1pt] \tabucline[1pt]{1-6}
        BMQHOA Mean &7438487.16&10276681.83&7774520.83&9075476 &9330322.16\\ \hline
        BMQHOA StDev. &29887.17&50507.35&34559.10&53168.02&46301.35\\ \hline 
        Mean Percent deviation from optimal &25.07&25.22&24.41&25.33&25.03\\[-1pt] \tabucline[1pt]{1-6}
    \end{tabu}
\end{table}

   % \vspace{1cm}
\begin{table}[h!]
    \centering
    \caption{Mean and StDev. of Uncorrelated Dataset} \label{uncorrelated-mean}
    \begin{tabu}{|c|[1pt]c|c|c|c|c|c|}
        \tabucline[1pt]{1-6} 
        Testcase & 1 & 2 & 3 & 4 & 5 \\ [-1pt] \tabucline[1pt]{1-6} 
        DGHS Mean &9147 &11238 &51019.5 &99036.16&448975 \\ \hline
        DGHS StDev. &0 &0 &437.85&1544.34&1135.46\\ \hline 
        Mean Percent deviation from optimal &0 &0 &6.39&10.47&20.34\\[-1pt] \tabucline[1pt]{1-6}
        BMQHOA Mean &8974.5 &10976.5 &47401.5 &91725.83&431259.66\\ \hline
        BMQHOA StDev. &147.24&154.37&841.75&1346.23&3049.43\\ \hline
        Mean Percent deviation from optimal &1.88&2.32&13.02&17.08&23.48\\[-1pt] \tabucline[1pt]{1-6}
    \end{tabu}

@@

    \caption{Mean and StDev. of Weakly Correlated Dataset} \label{weakly-mean}
    \begin{tabu}{|c|[1pt]c|c|c|c|c|c|}
        \tabucline[1pt]{1-6} 
        Testcase & 1 & 2 & 3 & 4 & 5 \\ [-1pt] \tabucline[1pt]{1-6} 
        DGHS Mean &1514 &1627.66&8907.33&17371.83&82681.33\\ \hline
        DGHS StDev. &0 &2.42&27.56&126.76&390.98\\ \hline 
        Mean Percent deviation from optimal &0 &0.38&1.59&3.76&8.33\\[-1pt] \tabucline[1pt]{1-6}
        BMQHOA Mean &1508.16&1613.66&8435.33&16539 &80900.66\\ \hline
        BMQHOA StDev. &6.82&16.74&60.60&133.95&970.71\\ \hline 
        Mean Percent deviation from optimal &0.38&1.24&6.81&8.37&10.31\\[-1pt] \tabucline[1pt]{1-6}
    \end{tabu}

@@

    \caption{Mean and StDev. of Strongly Correlated Dataset} \label{strongly-mean}
    \begin{tabu}{|c|[1pt]c|c|c|c|c|c|}
        \tabucline[1pt]{1-6} 
        Testcase & 1 & 2 & 3 & 4 & 5 \\ [-1pt] \tabucline[1pt]{1-6} 
        DGHS Mean &2391.66&2697 &13682.5 &26444.66&126448 \\ \hline
        DGHS StDev. &6.08&0 &60.05&240.84&615.61\\ \hline 
        Mean Percent deviation from optimal &0.22&0 &4.91&8.55&13.93\\[-1pt] \tabucline[1pt]{1-6}
        BMQHOA Mean &2327.33&2658.66&13334.66&25604 &123813.83\\ \hline
        BMQHOA StDev. &48.55&48.81&182.91&91.32&773.19\\ \hline
        Mean Percent deviation from optimal &2.90&1.42&7.33&11.46&15.72\\[-1pt] \tabucline[1pt]{1-6}
    \end{tabu}
\end{table}

\begin{table}[h!]
    \centering
    \caption{Mean percentage deviation from optimal across all datasets}\label{deviation-table}
    \begin{tabu}{|c|c|c|}
        \tabucline[1pt]{1-6} 
        & DGHS mean percentage deviation & BMQHOA mean percentage deviation \\ [-1pt] \tabucline[1pt]{1-6} 
        100 randomized items &0.12\% &4.17\% \\ \hline
        1000 randomized items &12.73\%&18.50\% \\\hline
        10k randomized items &22.78\%&25.01\% \\\hline
        Uncorrelated dataset &7.44\%&11.56\% \\\hline
        Weakly Correlated dataset &2.81\%&5.42\% \\\hline
        Strongly Correlated Dataset &5.52\%&7.77\% \\[-1pt] \tabucline[1pt]{1-6} 
    \end{tabu}
\end{table}

%100 randomized items mean and stdev graph

\begin{figure}[hbt!]
\centering
    \begin{tikzpicture}
        \begin{axis} [
            ybar = .05cm,
            bar width = 9pt,
            symbolic x coords={100 randomized, 1000 randomized, 10k randomized, Uncorrelated, Weakly, Strongly},
            x tick label style={font=\scriptsize,text width=1cm,align=left},
            ymin=0,
            ylabel = Percent deviation from optimal, 
            legend cell align={left},
            legend pos = north west,
            %ytick = data,+
            enlarge y limits = {value = .2, upper},
            enlarge x limits = {abs = 13pt}
        ]
        \addplot+[fill = blue] coordinates {
            (100 randomized, 0.12)
            (1000 randomized, 12.73)
            (10k randomized, 22.78)
            (Uncorrelated, 7.44)
            (Weakly, 2.81)
            (Strongly, 5.52)
        };
        \addplot+[fill = red] coordinates {
            (100 randomized, 4.17)
            (1000 randomized, 18.50)
            (10k randomized, 25.02)
            (Uncorrelated, 11.56)
            (Weakly, 5.42)
            (Strongly, 7.77)
        };

        \legend {DGHS, BMQHOA};
        \end{axis}
    \end{tikzpicture}
    \caption{Mean percentage deviation from optimal across all datasets} \label{deviation-graph}
    %\vfill
    \begin{tikzpicture}
        \begin{axis} [
            ybar = .05cm,
            bar width = 12pt,
            xmin = 1,
            xmax = 5,
            ymin=0,
            xlabel = Testcase,
            ylabel = Mean profit value,
            legend cell align={left},
            legend pos = north west,
            %ytick = data,
            y tick label style={
            /pgf/number format/1000 sep=},
            enlarge y limits = {value = .25, upper},
            enlarge x limits = {abs = .8}
        ]
        \addplot+ [
                error bars/.cd,
                    y dir=both,
                    % (changed from `y explicit` so the error bars are (clearly) visible
                    y explicit ,
            ] coordinates {
                (1, 4160.33) +- (0,3.5)
                (2, 2561) +- (0,0)
                (3, 5288) +- (0,19.667)
                (4,3535) +- (0,0)
                (5,1747) +- (0,0)
            };
        \addplot+ [
                error bars/.cd,
                    y dir=both,
                    % (changed from `y explicit` so the error bars are (clearly) visible
                    y explicit ,
            ] coordinates {
                (1, 3926.83) +- (0,40.27613023)
                (2, 2561) +- (0,0)
                (3, 4879) +- (0,46.18224767)
                (4,3360.66) +- (0,68.9627919)
                (5,1711.5) +- (0,25.71186497)
            };
        \legend {DGHS, BMQHOA};
        \end{axis}
    \end{tikzpicture}
    \caption{Mean of profit values for 100 randomized items} \label{100-graph}
\end{figure}

%1000+10k random items mean and stdev graph
\begin{figure}[hbt!]
\centering
    \begin{tikzpicture}
        \begin{axis} [
            ybar = .05cm,
            bar width = 12pt,
            xmin = 1,
            xmax = 5,
            ymin = 0,
            xlabel = Testcase,
            ylabel = Mean profit value,
            legend cell align={left},
            legend pos = north west,
            %ytick = data,
            y tick label style={
            /pgf/number format/1000 sep=},
            enlarge y limits = {value = .25, upper},
            enlarge x limits = {abs = .8}
        ]
        \addplot+ [
                error bars/.cd,
                    y dir=both,
                    % (changed from `y explicit` so the error bars are (clearly) visible
                    y explicit ,
            ] coordinates {
                (1, 156083.83) +- (0,830.04)
                (2, 118603.83) +- (0,1904.70)
                (3, 144070.00) +- (0,1343.77)
                (4, 109734.33) +- (0,1037.03)
                (5, 126366.17) +- (0,1236.73)
            };
        \addplot+ [
                error bars/.cd,
                    y dir=both,
                    % (changed from `y explicit` so the error bars are (clearly) visible
                    y explicit ,
            ] coordinates {
                (1, 145086.50) +- (0,1035.46)
                (2, 109876.33) +- (0,1540.63)
                (3, 136622.67) +- (0,2042.95)
                (4,101951.33) +- (0,1271.88)
                (5,118291.17) +- (0,799.79)
            };
        \legend {DGHS, BMQHOA};
        \end{axis}
    \end{tikzpicture}
\caption{Mean of profit values for 1000 randomized items} \label{1000-graph}
%\end{figure}

%10k random items mean and stdev graph
%\begin{figure}[hbt!]
%\centering
    \begin{tikzpicture}
        \begin{axis} [
            ybar = .05cm,
            bar width = 12pt,
            xmin = 1,
            xmax = 5,
            ymin = 0,
            xlabel = Testcase,
            ylabel = Mean profit value,
            %ytick = data,
            legend cell align={left},
            legend pos = north west,
            y tick label style={
            /pgf/number format/1000 sep=},
            enlarge y limits = {value = .25, upper},
            enlarge x limits = {abs = .8}
        ]
        \addplot+ [
                error bars/.cd,
                    y dir=both,
                    % (changed from `y explicit` so the error bars are (clearly) visible
                    y explicit ,
            ] coordinates {
                (1, 7681910.333) +- (0, 51555.40)
                (2, 10567302) +- (0, 23956.32)
                (3, 8014906) +- (0, 39449.15)
                (4, 9347061.67) +- (0, 56967.67)
                (5, 9583139.17) +- (0, 55816.61)
            };
        \addplot+ [
                error bars/.cd,
                    y dir=both,
                    % (changed from `y explicit` so the error bars are (clearly) visible
                    y explicit ,
            ] coordinates {
                (1, 7438487.17) +- (0, 29887.18)
                (2, 10276681.83) +- (0, 50507.36)
                (3, 7774520.83) +- (0, 34559.11)
                (4, 9075476.00) +- (0, 53168.02)
                (5, 9330322.17) +- (0, 46301.35)
            };
        \legend {DGHS, BMQHOA};
        \end{axis}
    \end{tikzpicture}
\caption{Mean of profit values for 10k randomized items} \label{10k-graph}
\end{figure}

%all correlations of items mean and stdev graph
\begin{figure}[hbt!]
    \centering
    \begin{tikzpicture}
        \begin{axis} [
            ybar,
            bar width = 12pt,
            width = 14cm,
            height = 6cm,
            xlabel = Testcase,
            ylabel = Mean profit value,
            xmin = 1,
            xmax = 5,
            ymin = 0,
            legend cell align={left},
            legend pos = north west,
            %x tick label style={rotate=45},
            xtick = data,
            ymin=0,
            %ytick = data,
            y tick label style={/pgf/number format/1000 sep=},
            enlarge y limits = {value = .25, upper},
            enlarge x limits = {abs = .8}
            %enlarge x limits = {abs = .8}
        ]
        \addplot+ [
                error bars/.cd,
                    y dir=both,
                    % (changed from `y explicit` so the error bars are (clearly) visible
                    y explicit ,
            ] coordinates {
                (1, 9147) +- (0, 0.00)
                (2, 11238.00) +- (0, 0.00)
                (3, 51019.50) +- (0, 437.85)
                (4, 99036.17) +- (0, 1544.34)
                (5, 448975.00) +- (0, 1135.46)
            };
        \addplot+ [
                error bars/.cd,
                    y dir=both,
                    % (changed from `y explicit` so the error bars are (clearly) visible
                    y explicit ,
            ] coordinates {
                (1, 8974.50) +- (0, 147.24)
                (2, 10976.50) +- (0, 154.37)
                (3, 47401.50) +- (0, 841.76)
                (4, 91725.83) +- (0, 1346.24)
                (5, 431259.67) +- (0, 3049.43)
            };
        \legend {DGHS, BMQHOA};
        \end{axis}
    \end{tikzpicture}
\caption{Mean of profit values for uncorrelated items} \label{uncorrelated-graph}
%\end{figure}

%\begin{figure}[hbt!]
    %\centering
    \begin{tikzpicture}
        \begin{axis} [
            ybar,
            bar width = 12pt,
            width = 14cm,
            height = 6cm,
            xlabel = Testcase,
            ylabel = Mean profit value,
            xmin = 1,
            xmax = 5,
            ymin=0,
            legend cell align={left},
            legend pos = north west,
            %x tick label style={rotate=45},
            xtick = data,
            %ytick = data,
            y tick label style={/pgf/number format/1000 sep=},
            enlarge y limits = {value = .25, upper},
            enlarge x limits = {abs = .8}
            %enlarge x limits = {abs = .8}
        ]
        \addplot+ [
                error bars/.cd,
                    y dir=both,
                    % (changed from `y explicit` so the error bars are (clearly) visible
                    y explicit ,
            ] coordinates {
                (1, 1514) +- (0, 0.00)
                (2, 1627.666667) +- (0, 2.422120283)
                (3, 8907.333333) +- (0, 27.56567914)
                (4, 17371.83333) +- (0, 126.7665834)
                (5, 82681.33333) +- (0, 390.9842282)
            };
        \addplot+ [
                error bars/.cd,
                    y dir=both,
                    % (changed from `y explicit` so the error bars are (clearly) visible
                    y explicit ,
            ] coordinates {
                (1, 1508.166667) +- (0, 6.823977335)
                (2, 1613.666667) +- (0, 16.74116683)
                (3, 8435.333333) +- (0, 60.6025302)
                (4, 16539) +- (0, 133.9596954)
                (5, 80900.66667) +- (0, 970.7196643)
            };
        \legend {DGHS, BMQHOA};
        \end{axis}
    \end{tikzpicture}
\caption{Mean of profit values for weakly correlated items} \label{weakly-graph}
%\end{figure}

%\begin{figure}[hbt!]
    %\centering
    \begin{tikzpicture}
        \begin{axis} [
            ybar,
            bar width = 12pt,
            xlabel = Testcase,
            ylabel = Mean profit value,
            width = 14cm,
            height = 6cm,
            xmin = 1,
            xmax = 5,
            ymin = 0,
            legend cell align={left},
            legend pos = north west,
            %x tick label style={rotate=45},
            xtick = data,
            %ytick = data,
            y tick label style={/pgf/number format/1000 sep=},
            enlarge y limits = {value = .25, upper},
            enlarge x limits = {abs = .8}
            %enlarge x limits = {abs = .8}
        ]
        \addplot+ [
                error bars/.cd,
                    y dir=both,
                    % (changed from `y explicit` so the error bars are (clearly) visible
                    y explicit ,
            ] coordinates {
                (1, 2391.666667) +- (0, 6.08824003)
                (2, 2697) +- (0, 0)
                (3, 13682.5) +- (0, 60.05580738)
                (4, 26444.66667) +- (0, 240.8407496)
                (5, 126448) +- (0, 615.61384)
            };
        \addplot+ [
                error bars/.cd,
                    y dir=both,
                    % (changed from `y explicit` so the error bars are (clearly) visible
                    y explicit ,
            ] coordinates {
                (1, 2327.333333) +- (0, 48.55375028)
                (2, 2658.666667) +- (0, 48.81666382)
                (3, 13334.66667) +- (0, 182.9160099)
                (4, 25604) +- (0, 91.32579044)
                (5, 123813.8333) +- (0, 773.1955553)
            };
        \legend {DGHS, BMQHOA};
        \end{axis}
    \end{tikzpicture}
\caption{Mean of profit values for strongly correlated items} \label{strongly-graph}
\end{figure}
